### 2021-04-28 Chapter-5/Chapter-5.tex
Updates from Overleaf

Third, while many existing tools can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}. There are some tools~\cite{182946,Chattopadhyay:2017:QIL:3127041.3127044} that can quantify the information leakage. Those tools can give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero. But those tools can not tell software developers how serious each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage. The best way to estimate each leakage's severe level is to exploit the leakage and recover the information. However, the process itself is very tedious and needs a lot of domain knowledge.

@@

\subsection{Threat Model and Math Notation}

@@

      \begin{tabular}{cccccccccc}
        \toprule
        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
        \midrule
        0              & A &   &   &   &   &                 \\
        1              &   & A &   &   &   &                 \\
        2              &   &   & A &   &   &                 \\
        3              &   &   &   & A &   &                 \\
        4              &   &   &   &   & A &                 \\
        5              &   &   &   &   &   & A &             \\
        6              &   &   &   &   &   &   & A           \\
        7              &   &   &   &   &   &   &   & A       \\
        \bottomrule
      \end{tabular}%
    }
  \end{minipage}
  \caption{A serious leakage.}\label{chapter5:fig:example1}
\end{figure}

@@

\ctool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \ctool{} may have the coverage problem and can miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs. For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities. However, \ctool{} is not designed to find side-channel vulnerabilities. The goal of \ctool{} is to pick up those really serious side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is the main limitation of \ctool{}. However, users of \ctool{} should be aware of the code coverage problem.

>>>>

Third, while many existing tools can detect side-channel leakages, few of them can assess how severity level of those vulnerabilities~\cite{203878,182946,Brotzman19Casym,236338,217537,Wichelmann:2018:MFF:3274694.3274741}. There are some tools~\cite{182946,Chattopadhyay:2017:QIL:3127041.3127044} that can quantify the information leakage. Those tools can give an upper bound estimation of each leakage site, which is useful to justify the software is secure if the reported leakage is zero. But those tools can not tell software developers how severe each leakage site would be because of the over-approximation they apply when they estimate the amount of leakage. The best way to estimate each leakage's severe level is to exploit the leakage and recover the information. However, the process itself is very tedious and needs a lot of domain knowledge.

@@

\subsection{Threat Model and Notation}

@@

      \begin{tabular}{cccccccccc}
        \toprule
        \diagbox{S}{T} & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & ... \\
        \midrule
        0              & A &   &   &   &   &                 \\
        1              &   & A &   &   &   &                 \\
        2              &   &   & A &   &   &                 \\
        3              &   &   &   & A &   &                 \\
        4              &   &   &   &   & A &                 \\
        5              &   &   &   &   &   & A &             \\
        6              &   &   &   &   &   &   & A           \\
        7              &   &   &   &   &   &   &   & A       \\
        \bottomrule
      \end{tabular}%
    }
  \end{minipage}
  \caption{A severe leakage.}\label{chapter5:fig:example1}
\end{figure}

@@

\ctool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \ctool{} may have the coverage problem and can miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control-flow with various inputs. For other libraries like graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities. However, \ctool{} is not designed to find side-channel vulnerabilities. The goal of \ctool{} is to pick up those really severe side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is the main limitation of \ctool{}. However, users of \ctool{} should be aware of the code coverage problem.
